\chapter{Syntax of \lang{}}
This chapter describes the different kinds of parser generators and analyses what features they have, to be able to make a conclusion for which one is the most suitable for this project. Afterwards, a language for describing syntax is presented, and then the syntax and grammar of \lang{} is presented and explained. 
\input{sections/Syntax/ParserGenerators.tex}

\subsection{EBNF notation}
In parser generators like SableCC, the syntax definition is split into several parts. The first part is a token definition section. In this section, common tokens that will be used in the actual definition of the syntax are defined. Usually, the section looks something like this: 

\begin{figure}[H]
    \centering
    \begin{lstlisting}[]
    ...
    mod = '%';
    lparen = '(';
    rparen = ')';
    numval = '-'? digit*;
    newline = (cr | lf | cr lf)+;
    id = letter(letter|digit)*;
    textval = '"' [any - '"']* '"';
    blank = space*;
    comment = '/' '*'[any - ['*' + '/']]* '*' '/';
    \end{lstlisting}
    \caption{Snippet from the Tokens section of the grammar of \lang{} in EBNF}
    \label{fig:EBNFtoken}
\end{figure}

This section mainly exists to unclutter the syntax definition that follows. 
The syntax definition consists of a collection of productions. A production is a left-hand side(LHS) which can be transformed into a right-hand side(RHS). These productions are also called rewriting rules.

The "|" is a way of writing alternatives in a production, so that it can be rewritten as multiple things. It is written like this:

\begin{figure}[H]
    \centering
    \begin{lstlisting}[]
    ...
    type    = num
            | bool
            | text
            | id;
    ...
    \end{lstlisting}
    \caption{Snippet from the Productions section of the grammar of \lang{} in EBNF}
    \label{fig:EBNFalt}
\end{figure}


The LHS is always a nonterminal. A nonterminal is a syntactic part that can be transformed into a terminal symbol by being put through a series of productions.
A terminal symbol is the final point of a production. For example, a "val" nonterminal, denoting a value of some kind, might end up being evaluated into a number(num) or string("text") in \lang{}. 



\input{sections/Syntax/OurSyntax.tex}
\input{sections/Syntax/FormalGrammar.tex}