    prog        =   global* maindcl newline? classdcl*

    global      =   vardcl newline

    maindcl     =   main begin newline stmt* end

    classdcl    =   newline eclass id inherit? begin newline classbody* end

    classbody   =   vardcl newline                                                            
                |   eventdcl newline                                                
                |   dcl func id lparen formalparam? rparen begin funcbody end newline

    funcbody    =   newline stmt* return

    return      =   {returnid} treturn bexpr newline
                |   {empty}                                                 


    stmt        =   vardcl newline                      
                |   set id to bexpr newline               
                |   for id upto bexpr do [a]:newline stmt* end [b]:newline 
                |   for id downto bexpr do [a]:newline stmt* end [b]:newline
                |   while bexpr do [a]:newline stmt* end [b]:newline  
                |   funcdotcall newline         
                |   ifstmt newline                      

    vardcl      =   dcl type id         
                |   dcl type id to bexpr      
                |   dcl list of type id      

    ifstmt      =   if bexpr then newline stmt* elsestmt? end

    elsestmt    =   else newline stmt*
                |   {elseif} else if bexpr then newline stmt* elsestmt?


    bexpr       =   bexpr or bterm             
                |   bterm                   

    bterm       =   bterm and relation 
                |   relation

    relation    =   expression equals expression
                |   expression notequals expression
                |   expression greater expression
                |   expression less expression       
                |   expression greaterequals expression 
                |   expression lessequals expression   
                |   expression 

    expression  =   expression minus term
                |   expression plus term
                |   term


    term        =   term divide [right]:factor  
                |   term mult [right]:factor  
                |   term mod [right]:factor  
                |   unary               

    unary       =   minus factor 
                |   not factor
                |   factor  

    factor      =   val
                |   id
                |   funcdotcall
                |   iddotcall
                |   lparen bexpr rparen

    type        =   num  
                |   bool     
                |   text                        
                |   id   

    val         =   numval
                |   textval
                |   boolval
                |   this
                |   new id lparen actualparam? rparen

    funccall    =   id lparen actualparam? rparen


    actualparam =   bexpr
                |   {mulparam} bexpr comma [rest]:actualparam               {-> [bexpr.expr, rest.expr]};

    formalparam {-> param*}  =   {singleparam} type id                                  {-> [New param.formal(type.type, id)]}
                            |   {mulparam} type id comma formalparam                    {-> [New param.formal(type.type, id), formalparam.param]};

    funcdotcall {-> call}   =   {mulcall} singlecall dot multicallfunc                  {-> New call.dot(singlecall.call, [multicallfunc.call])}
                            |   {single} funccall                                       {-> funccall.call};

    iddotcall {-> call}     =   {mulcall} singlecall dot multicallid                    {-> New call.dot(singlecall.call, [multicallid.call])};

    singlecall  {-> call}   =   {idcall} id                                             {-> New call.var(id)}
                            |   {funccall} funccall                                     {-> funccall.call};

    multicallid {-> call*}  =   {single} id                                             {-> [New call.var(id)]}
                            |   {multi} singlecall dot [rest]:multicallid                 {-> [singlecall.call, rest.call]};

    multicallfunc   {-> call*}  =   {single} funccall                                   {-> [funccall.call]}
                                |   {multi} singlecall dot [rest]:multicallfunc             {-> [singlecall.call, rest.call]};


    inherit     {-> inherit}    =    is type                                            {-> New inherit(type)};

    eventdcl    {-> pdcl}   =   id lparen formalparam* rparen do newline baseconstr? [body]:stmt* end          {-> New pdcl.event(id, [formalparam.param], baseconstr.base, [body.stmt])};

    baseconstr  {-> base}   =   tbase lparen actualparam? rparen newline                {-> New base.base([actualparam.expr])};